---
title: "Package Name: packageTemplateHC"
author: "Halimat Chisom Atanda"
date: "2022-10-17"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{packageTemplateHC}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Package Description

This package was created from the `bugsigdbr` package in Bioconductor.
It imports data from BugSigDB and filters it based on location and
condition.

Here's a simple breakdown of how the `packageTemplateHC` works:

-   loads the library of `bugsigdbr`

-    imports all the data from [BugSigBD](bugsigdb.org)

-   Filters extracted data based on location study and condition type

-   Returns a filtered dataframe

## Using `packageTemplateHC`

To use this package, you must:

-   be interested in a particular study location and condition, and

-   have `bugsigdbr` package installed

There are over 60 different locations and over 180 conditions in the
dataset for which you can use to filter.

The package accepts two arguments, a and b. a takes location of subjects
and b takes condition, both as strings.

E.g. a could be "United States of America", "Denmark," "Italy," etc.

b could be "adenoma," "obesity," "high fat diet," "gestational
diabetes," etc.

The output of this package is a simple filtered dataframe containing all
entries of the location and condition of choice.

## Code Description

The first line of code defines the function.
The next loads the `bugsigdbr` package.
Then, data is imported into a dataframe, "`biodata`"
The next lines defines each argument in the function, and final command prints the filteres dataframe.

```{r}
# function to print a dataframe with specified country and condition

packageTemplateHC <- function(a,b) {
	library(bugsigdbr)
	biodata <- importBugSigDB()
	df <- subset(biodata, `Location of subjects` == a &
               Condition == b)
  
	  print(df)
}
```

## Example

```{r echo=TRUE}
filteredUSAadenoma <- packageTemplateHC("United States of America", "adenoma")

dim(filteredUSAadenoma)
```

```{r echo=TRUE}
filteredDenmarkAdenoma <- packageTemplateHC("Denmark", "adenoma")

dim(filteredDenmarkAdenoma)
```


